---
title: "Monthly Budgeting Information"
author: "Beka"
date: "8/11/2021"
output:
  html_document:
    df_print: paged
  pdf_document:
    df_print: kable
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
source(knitr::purl("bei_budget.rmd", quiet=TRUE))
```

# Monthly Operating Income and Expenses, BEI January - July 2021

## Monthly Expenses

* For an overview of expenses by month and category see [Monthly Expense Datatable](https://rpubs.com/BEI_BB/monthly_expenses)
  * this table provides an overview of all expenses, sorted by expense category and month.

* For a summary of monthly expenses by category for the period of January - July 2021 see [Monthly Expenses by Category](https://rpubs.com/BEI_BB/expenses_summary)
  * this table provides information on the minimum, average, and maximum amounts spent in each category, along with the standard error around the estimate of the average amount spent.


### Monthly Expenses Graphs

#### All expenses, including farm lease expense which includes owners draws

```{r echo=FALSE, message=FALSE}
all_expenses_plot
``` 


#### All expenses minus farm lease expenses

```{r echo=FALSE, message=FALSE}
no_farmlease_expenses_plot
``` 


#### All expenses below $10k

```{r echo=FALSE, message=FALSE}
below_10k_expenses_plot
```


#### Average Monthly Expenses:

```{r echo=FALSE, message=FALSE}
average_monthly_expenses
```

* **NOTE** Average expenses shown here do not include depreciation (total of 45500 over the period January - July 2021) or interest expense (121.36 total over the period of January - July 2021).


## Monthly Income

* For an overview of income by month and category see [Monthly Income Datatable](https://rpubs.com/BEI_BB/monthly_income)
  * this table shows income sorted by month and income category. 


* For summary statistics on monthly income by category (for the period of January - July 2021) see [Average Income by Category](https://rpubs.com/BEI_BB/average_income)
  * this table provides information on the minimum, average, and maximum amounts of income in each category, along with the standard error around the estimate of the average.



### Monthly Income Graph

#### All income, minus 'other' category ($44,776.93 total, from tax return and deposit from Hippo)

```{r echo=FALSE, message=FALSE}
all_income_plot
``` 


#### Average monthly income (minus the 'other' category):

```{r echo=FALSE, message=FALSE}
average_monthly_income
```


#### Average monthly income less expenses (excluding the 'other' income and 'other' expenses):

```{r echo=FALSE, message=FALSE}
average_monthly_income - average_monthly_expenses
``` 


#### Total 'other' income less 'other' expenses for the period January - July 2021: **-844.43**


### Spending projection 
* **NOTE** this is simply the average spent over the period January - July 2021

```{r echo=FALSE, message=FALSE}
as.data.frame(averages[order(-averages$average),])
``` 


